\papertitle

### 2014-03-18 final-report/paper.tex
Add todos

@@

\textbf{Tooltip Information:} TODO

@@

We explore a simple join query we performed on one million tuples extracted from Twitter data. This query joins Twitter followers and followees by user ID. The query written in SQL is expressed below.

@@

The resulting \graph visualization is displayed in ~\ref{fig:TODO}. The user will navigate the \graph visualization in the browser panel in the next case studies to identify several performance symptoms.

>>>>

\todo{write me}

@@

\textbf{Tooltip Information:} \todo{write me}

@@

We explore a simple join query we performed on one million tuples extracted from the Twitter user graph. This query joins Twitter followers and followees by user ID. The query can be written in SQL as expressed below.

@@

The resulting \graph visualization is displayed in Figure~\ref{fig:TODO}. The user will navigate the \graph visualization in the browser panel in the next case studies to identify several performance symptoms.
